Data Analysis

### 2023-04-13 ms1_data_analysis.Rmd
Visualizations for the SLA model mostly done. Getting ready to impolement random forest models for the rest of the treatments.

# Subset a data-set to only control and treatment plots
subDat <- dwbRichF %>%
  filter(treatment %in% subsetVars)

@@

# Get the delta data ready for th e given subset vars (comparison)
subsetVars <- c("c", "i")

@@

# Predator --------------------------
pslap <- predictAndVisualize(p.mod, 
                    p.dD,
                    "lsla.d",
                    n = 100,
                    titlestring = "Predator - A",
                    ylabstring = "Log-response ratio of total biomass.",
                    xlabstring = "Log(SLA)")

@@

# Co-variates
psitep <- predictAndVisualize(p.mod, 
                    p.dD,
                    "fsite",
                    n = 100,
                    titlestring = "Predator - B",
                    ylabstring = "Log-response ratio of total biomass.",
                    xlabstring = "Sites")

plabup <- predictAndVisualize(p.mod, 
                    p.dD,
                    "labu",
                    n = 100,
                    titlestring = "Predator - C",
                    ylabstring = "Log-response ratio of total biomass.",
                    xlabstring = "Log(stem number)")

# Insecticide-----------------------
ilabup <- predictAndVisualize(i.mod, 
                    i.dD,
                    "labu",
                    n = 100,
                    titlestring = "Insecticide - C",
                    ylabstring = "Log-response ratio of total biomass.",
                    xlabstring = "Log(stem number)")

# Extra herbivory-------------------
hsitep <- predictAndVisualize(h.mod, 
                    h.dD,
                    "fsite",
                    n = 100,
                    titlestring = "Herbivory - A",
                    ylabstring = "Log-response ratio of total biomass.",
                    xlabstring = "Sites")

hwaterp <- predictAndVisualize(h.mod, 
                    h.dD,
                    "water.cont",
                    n = 100,
                    titlestring = "Herbivory - A",
                    ylabstring = "Log-response ratio of total biomass.",
                    xlabstring = "Water content")

hlabup <- predictAndVisualize(h.mod, 
                    h.dD,
                    "labu",
                    n = 100,
                    titlestring = "Herbivory - B",
                    ylabstring = "Log-response ratio of total biomass.",
                    xlabstring = "Log(stem number)")

hlrrslap <- predictAndVisualize(h.mod, 
                    h.dD,
                    "lrrsla",
                    n = 100,
                    titlestring = "Herbivory - B",
                    ylabstring = "Log-response ratio of total biomass.",
                    xlabstring = "LRR SLA")

# Plot
ggpubr::ggarrange(pslap, psitep, plabup)

ggpubr::ggarrange(ilabup)

ggpubr::ggarrange(hwaterp, hsitep, hlabup, hlrrslap)

>>>>

# ENCLOSED IN THE get_ready_for_the_sla_analyses
# Subset a data-set to only control and treatment plots 
subDat <- dwbRichF %>%
  filter(treatment %in% subsetVars)

@@

# Get the delta data ready for th e given subset vars (comparison)
subsetVars <- c("c", "i")
source('code/get_data_ready_for_the_sla_analyses.R')

@@

# Predator --------------------------
pslap <- predictAndVisualize(p.mod, 
                    p.dD,
                    "lsla.d",
                    n = 100,
                    titlestring = "Predator - Specific Leaf Area",
                    ylabstring = "Log-response ratio of total biomass.",
                    xlabstring = "Log(SLA)")

@@

# Co-variates
psitep <- predictAndVisualize(p.mod, 
                    p.dD,
                    "fsite",
                    n = 100,
                    titlestring = "Predator - Site",
                    ylabstring = "Log-response ratio of total biomass.",
                    xlabstring = "Sites")

plabup <- predictAndVisualize(p.mod, 
                    p.dD,
                    "labu",
                    n = 100,
                    titlestring = "Predator - Abundance",
                    ylabstring = "Log-response ratio of total biomass.",
                    xlabstring = "Log(stem number)")
prichp <- predictAndVisualize(p.mod, 
                    p.dD,
                    "richness",
                    n = 100,
                    titlestring = "Predator - Richness",
                    ylabstring = "Log-response ratio of total biomass.",
                    xlabstring = "Number od species")
plrrslap <- predictAndVisualize(p.mod, 
                    p.dD,
                    "lrrsla",
                    n = 100,
                    titlestring = "Predator - LRR SLA",
                    ylabstring = "Log-response ratio of total biomass.",
                    xlabstring = "LRR SLA")

# Insecticide-----------------------
ilabup <- predictAndVisualize(i.mod, 
                    i.dD,
                    "labu",
                    n = 100,
                    titlestring = "Insecticide - Abundance",
                    ylabstring = "Log-response ratio of total biomass.",
                    xlabstring = "Log(stem number)")

# Extra herbivory-------------------
hsitep <- predictAndVisualize(h.mod, 
                    h.dD,
                    "fsite",
                    n = 100,
                    titlestring = "Herbivory - Site",
                    ylabstring = "Log-response ratio of total biomass.",
                    xlabstring = "Sites")

hwaterp <- predictAndVisualize(h.mod, 
                    h.dD,
                    "water.cont",
                    n = 100,
                    titlestring = "Herbivory - Water Content",
                    ylabstring = "Log-response ratio of total biomass.",
                    xlabstring = "Water content")

hlabup <- predictAndVisualize(h.mod, 
                    h.dD,
                    "labu",
                    n = 100,
                    titlestring = "Herbivory - Abundance",
                    ylabstring = "Log-response ratio of total biomass.",
                    xlabstring = "Log(stem number)")

hlrrslap <- predictAndVisualize(h.mod, 
                    h.dD,
                    "lrrsla",
                    n = 100,
                    titlestring = "Herbivory - LRR SLA",
                    ylabstring = "Log-response ratio of total biomass.",
                    xlabstring = "LRR SLA")

# Fungicide

fwaterp <- predictAndVisualize(f.mod, 
                    f.dD,
                    "water.cont",
                    n = 100,
                    titlestring = "Fungicide - Water Content",
                    ylabstring = "Log-response ratio of total biomass.",
                    xlabstring = "Water content")

fsitep <- predictAndVisualize(f.mod, 
                    f.dD,
                    "fsite",
                    n = 100,
                    titlestring = "Fungicide - Site",
                    ylabstring = "Log-response ratio of total biomass.",
                    xlabstring = "Site")

frichp <- predictAndVisualize(f.mod, 
                    f.dD,
                    "richness",
                    n = 100,
                    titlestring = "Fungicide - Richness",
                    ylabstring = "Log-response ratio of total biomass.",
                    xlabstring = "Number of species per plot")

# Plot
ggpubr::ggarrange(pslap +
                    scale_y_continuous(limits = c(-5, 10)),
                  fwaterp + 
                    scale_y_continuous(limits = c(-5, 10)), 
                  hwaterp + 
                    scale_y_continuous(limits = c(-5, 10)), 
                  nrow = 1, legend = F)
ggpubr::ggarrange(psitep + 
                    scale_y_continuous(limits = c(-5, 10)), 
                  fsitep + 
                    scale_y_continuous(limits = c(-5, 10)), 
                  hsitep + 
                    scale_y_continuous(limits = c(-5, 10)), 
                  nrow = 1,legend = F)
ggpubr::ggarrange(prichp + 
                    scale_y_continuous(limits = c(-5, 10)), 
                  frichp + 
                    scale_y_continuous(limits = c(-5, 10)), 
                  nrow = 1, legend = F)
ggpubr::ggarrange(plabup + 
                    scale_y_continuous(limits = c(-5, 10)), 
                  ilabup + 
                    scale_y_continuous(limits = c(-5, 10)), 
                  hlabup + 
                    scale_y_continuous(limits = c(-5, 10)), 
                  nrow = 1, legend = F)
ggpubr::ggarrange(plrrslap +
                    scale_y_continuous(limits = c(-5, 10)), 
                  hlrrslap + 
                    scale_y_continuous(limits = c(-5, 10)), 
                  nrow = 1, common.legend = T)
